Appendix 2: Example of index standardization of fishery-independent survey data with sdmTMB

### 2022-01-05 doc/appendix-pcod-sdmTMB.Rmd
Copy edit appendices
Update appendix-pcod-sdmTMB.Rmd
EW edits

---
title: "Appendix 2: example of index standardization of fishery-independent survey data with sdmTMB"
output:
  pdf_document:
    highlight: tango
---

@@

The above example used the default `bias_correct = FALSE` in `get_index()`. This is fine for experimentation or a quick example, but will be biased due to the nonlinear (`exp()`) transformation of the random effects. Setting `bias_correct = TRUE` implements the generic by his correction algorithm that should correct for this, but can take considerable time and memory.

>>>>

---
title: "Appendix 2: Example of index standardization of fishery-independent survey data with sdmTMB"
output:
  pdf_document:
    highlight: tango
---

@@

The above example used the default `bias_correct = FALSE` in `get_index()`. The `bias_correct` argument is a feature of TMB for models with random effects, and more detils can be found in the TMB documentation [https://github.com/kaskr/adcomp/wiki](https://github.com/kaskr/adcomp/wiki) or [Thorson & Kristensen (2016)](https://www.sciencedirect.com/science/article/abs/pii/S0165783615301399?via%3Dihub). Leaving `bias_correct = FALSE` is fine for experimentation or a quick example, but will be biased due to the nonlinear (`exp()`) transformation of the random effects. Setting `bias_correct = TRUE` implements the generic by his correction algorithm that should correct for this, but can take considerable time and memory.
